Timeliness of security updates for Android

### 2014-08-05 securityupdates.tex
Update figures and figures updater script
Include figure showing difference between DA and GP data

The data from Device Analyzer (DA) we want to use to investigate the proportion of devices exposed to different vulnerabilities is the OS version.
Unfortunately there is no authoritative source of OS version information and so we cannot check directly whether our data is representative.
However Google has published API version information every month since December 2009 and we have collated this information.\footnote{\url{https://www.cl.cam.ac.uk/~drt24/android/versiondistribution/}}
While API versions are too coarse grained to use for security update detection they are closely related to OS versions and so if the DA data on API versions is similar to the Google Data on API versions then the DA data on OS versions should be representative.
Figure \ref{fig:play_api} shows the data Google and Figure \ref{fig:da_api} and they appear similar. %TODO we want a statistical metric to claim this strongly with.
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/googleplayapi}
 \caption{Google Play data on proportion of devices running different Android API versions}
 \label{fig:play_api}
\end{figure}
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/da_norm_api}
 \caption{Google Play data on proportion of devices running different Android API versions}
 \label{fig:da_api}
\end{figure}

>>>>

The data from Device Analyzer (DA) we want to use to investigate the proportion of devices exposed to different vulnerabilities is the OS version.
Unfortunately there is no authoritative source of OS version information and so we cannot check directly whether our data is representative.
However Google has published API version information every month since December 2009 and we have collated this information.\footnote{\url{https://www.cl.cam.ac.uk/~drt24/android/versiondistribution/}}
While API versions are too coarse grained to use for security update detection they are closely related to OS versions and so if the DA data on API versions is similar to the Google Data on API versions then the DA data on OS versions should be representative.
Figure \ref{fig:play_api} shows the data from Google and Figure \ref{fig:da_api} shows the data from Device Analyzer and they appear similar.
Figure \ref{fig:da_gp_comp_diff} shows the difference between Figures \ref{fig:play_api} and \ref{fig:da_api}.
It shows that the Device Analyzer data systematically overestimates the prevalence of new API versions and underestimates the prevalence of old API versions.
This means that the OS version information from Device Analyzer is likely to be overestimating the prevalence of new OS versions and hence our results are a conservative estimate of the security of Android.
%TODO we want a statistical metric to claim this strongly with.
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/googleplayapi}
 \caption{Google Play data on proportion of devices running different Android API versions}
 \label{fig:play_api}
\end{figure}
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/norm_api_gpcomp}
 \caption{Device Analyzer data on proportion of devices running different Android API versions}
 \label{fig:da_api}
\end{figure}
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/api_gpcomp_diff}
 \caption{Difference between Device Analyzer and Google Play data on the proportion of devices running different Android API versions}
 \label{fig:da_gp_comp_diff}
\end{figure}
